CAP-423 - Ciência de Dados Geoespaciais

### 2024-12-09 docs-site/code.Rmd

% Code

## Leitura dos dados produzidos em R

## Carregand

The packages necessary for this analysis..

```{r}
library(readr)
```

## Data import

Let's first import the data.

```{r message=FALSE, warning=FALSE}
data <- read_delim("data/data.csv", delim = ";")
data
```

## Data tidy

Data wrangling here.

## Data transformation

We need to do some transformations, create new variables, etc.

## Data visualization

Produce some plots to understand the data

## Data analysis

Modeling

## Manuscript-ready plots

This could be shown here or in a separate webpage.

>>>>

% Leitura dos dados produzidos em R

## Carregando os pacotes {-}

```{r}
library(terra)
library(sf)
library(leaflet)
```

## Leitura dos dados {-}

```{r message=FALSE, warning=FALSE}
agri_poll <- sf::st_read("../croplands-classification/data/derived/SENTINEL-2_MSI_028022_2021-06-26_2021-06-26_class_masked-bin.json")
agri_poll
```

## Visualização dos dados {-}

```{r message=FALSE, warning=FALSE}
plot(agri_poll)
```

## Visualização interativa com leaflet  {-}

Reprojeção para WGS 84

```{r message=FALSE, warning=FALSE}
sf::st_crs(agri_poll) <- "+proj=aea +lat_0=-12 +lon_0=-54 +lat_1=-2 +lat_2=-22 +x_0=5000000 +y_0=10000000 +ellps=GRS80 +units=m +no_defs"

agri_poll <- sf::st_transform(agri_poll, 4326)
```

Filtrando somente os poligonos de agricultura e usando o Leaflet para visualizar.

```{r message=FALSE, warning=FALSE}

agri_poll <- agri_poll[agri_poll$label == "Agricultura",]

leaflet(agri_poll) |>
  addTiles() |> 
  addPolygons(popup = ~label)
```
